A Bayesian Framework for Learning Regular Expressions

### 2012-12-09 paper/paper.tex

We note that in cases 16 (S = \{`yyyt', `yt', `yyyt', `yyyt', `yt'\}, s= `yyyyyt'), 17 (S = \{`jojojojo', `jojojojo', `jojojojo'\}, s = `jojo'), and 18 (S = \{`twtwtw', `twtwtw', `twtwtw'\}, s =  `tw'), it is clear that the model more strongly prefers the use of the Kleene star. However, because this same parameter in part controls for wildcards, lowering it reduces performance on many other cases.

This suggests that our model's parameter $\beta$ may in fact be better represented by more than one variable in human decision making.

We also observe that in such cases, there was a relatively small set of probable hypotheses, and that any favoring of smaller hypotheses was magnified by this fact. 
\section{Conclusion and Future Work}
Despite the number of ways in which our model might be improved mentioned above,  it remains highly implausible that the brain generates its set of candidate hypotheses by ever considering even $2^n$ hypotheses in the first level of beam search we perform, much less more than that. Doing so would be highly inefficient: the number of implausible hypotheses generated would in most cases be far greater than the number of `good' hypotheses. Far more plausible a priori is the hypothesis that the brain uses of number of heuristics to generate a certain set of candidate hypothesis, and then uses some process analogous to Bayesian inference to select among those hypotheses. To shed light on how this hypothesis selection process may occur, we designed an experiment in which candidates chose among a number of possible rules to explain a set of strings S, but have yet to gather enough data to reach any significant conclusions.

Further experiments could be conducted to determine what heuristics may be at work in the hypothesis generation process. For any set of candidate heuristics, it will remain to be determined whether or not such heuristics are at some point learned. Clearly some semantic considerations are at work in human pattern recognition on strings: cat and mat but not qat are meaningful english words; `ao' and `eo' and `io' begin with vowels unlike `xo'. (This experiment was designed to avoid such candidate hypotheses.) One partial solution to this sort of problem would be to permit different varieties of wildcards (e.g., for vowels) beyond just those for number and alphabetical character. Here, though, we risk fitting experimental data at the expense of more general having a more general model, since such wildcards would have to be hardcoded.

>>>>

We note that in cases 16 (S = \{`yyyt', `yt', `yyyt', `yyyt', `yt'\}, s= `yyyyyt'), 17 (S = \{`jojojojo', `jojojojo', `jojojojo'\}, s = `jojo'), and 18 (S = \{`twtwtw', `twtwtw', `twtwtw'\}, s =  `tw'), it is clear that the model more strongly prefers the use of the Kleene star. Here, the prior on the hypothesis is so low that the difference in the likelihood of the base hypothesis as compared to a hypothesis with fewer states and more loops that the posterior probability becomes relatively unlikely. Future work could better determine how this term should be set. However, because this same parameter in part controls for wildcards, lowering it reduces performance on many other cases.

We also observe that in such cases, there was a relatively small set of probable hypotheses, and that any favoring of smaller hypotheses was magnified by this fact.

\section{Conclusion and Future Work}
Despite the number of ways in which our model might be improved mentioned above,  it remains highly implausible that the brain generates its set of candidate hypotheses by ever considering even $2^n$ hypotheses in the first level of beam search we perform, much less more than that. Doing so would be highly inefficient: the number of implausible hypotheses generated would in most cases be far greater than the number of `good' hypotheses. Far more plausible a priori is the hypothesis that the brain uses of number of heuristics to generate a certain set of candidate hypothesis, and then uses some process analogous to Bayesian inference to select among those hypotheses. To shed light on how this hypothesis selection process may occur, we designed an experiment in which candidates chose among a number of possible rules to explain a set of strings S, but have yet to gather enough data to reach any significant conclusions.

Further experiments could be conducted to determine what heuristics may be at work in the hypothesis generation process. For any set of candidate heuristics, it will remain to be determined whether or not such heuristics are at some point learned. Clearly some semantic considerations are at work in human pattern recognition on strings: cat and mat but not qat are meaningful english words; `ao' and `eo' and `io' begin with vowels unlike `xo'. (This experiment was designed to avoid such candidate hypotheses.) One partial solution to this sort of problem would be to permit different varieties of wildcards (e.g., for vowels) beyond just those for number and alphabetical character. Here, though, we risk fitting experimental data at the expense of more general having a more general model, since such wildcards would have to be hardcoded. The model could also be extended to include something like a successor function, which would allow the model to recognize `efg' as a member of the set \{`abc',`bcd',`cde',`def'\}.
